Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-10 paper/main.tex
add linkedin ref

The pictures in S3 are based on two essential formats, which is STAC and COG. The satellites generate them everyday. 
World Bank organized the global night lights project to store these files in S3. When it comes to deal with the satellite 
imagery, Python has a lot of easy libraries for geospatial calculating. GDAL is the most useful one. 
It is integrated with Python very well, and is very good at reading and writing raster or vector geospatial file formats.

@@

    \item Huajie Xu: FE
    \item Shengzhu Wang(Simon): BE. Implemented part of the backend Java code. Quited the team early without participating in writing.
    \item SiXiang Xiong(Tom): BE, Testing
    \item Wenjie Tong: Data Researcher, Testing
\end{itemize}

>>>>

The pictures in S3 are based on two essential formats, which is STAC and COG. The satellites generate them everyday. 
World Bank organized the global night lights project to store these files in S3. When it comes to deal with the satellite 
imagery, Python has a lot of easy libraries for geospatial calculating. GDAL is the most useful one. 
It is integrated with Python very well, and is very good at reading and writing raster or vector geospatial file formats.
There are also some people opening the processing sourcecode \cite{Howtopro5:online}.

@@

    \item Huajie Xu: FE
    \item Shengzhu Wang(Simon): BE. Implemented part of the backend Java code. Quited the team early without participating in writing.
    \item SiXiang Xiong(Tom): BE, Testing
    \item Wenjie Tong: UI designer,Data Researcher, Testing.
    In my part of this project, I am playing a role of UI designer,Data Researcher and function tester. 
    Implementing part of the contribution:
    UI desgin is based on functions to develop the web pages.
    Data reseach regarding with World Bank---Light Every Light doucument,and I have done further study to understand the related knowledge about DSMP-OLS and VIISR-DNB data.
    I will take a part of testing task to ensure the functionality of our project.
    Writing part:
    I have wrote the Light Every night part of paper in solution summary. And in proposed solution,I have wrote part of process the data.

\end{itemize}
